---
title: "Iteration and List Columns"
author: "Vanessa Dinh"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

set.seed(1)
```

# Lists

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

Let's look at a list

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

Accessing list items

```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```

## Loops

Let's make a for loop to take the mean and SD of four samples from a normal distribution
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

Here's my function

```{r}
mean_and_sd = function(x) {
  
  
   if(!is.numeric(x)) {
    stop("Z scores only work for numbers")
  }
  
  if(length(x) < 3) {
    stop("Z scores really only work if you have three or more numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
}
```

Let's try to make this work

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Let's try a for loop instead

```{r}
output = vector("list", length = 4)

for(i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norms[[i]])
  
}

output
```

## can we map??

we can map!!

```{r}
map(list_norms, mean_and_sd)
```

so ... what about other functions?

```{r}
map(list_norms, median)

```

map variants... (gives nice vector)

```{r}
map_dbl(list_norms, median) # nice vector instead of separate output

map_df(list_norms, mean_and_sd) # collapses to make nice dataframe
```

## list columns ...

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )

listcol_df[["samp"]]

output = map(listcol_df[["samp"]], mean_and_sd)
```

can we add list columns and then what

```{r}
listcol_df %>% 
  mutate(
    m_sd = map_df(samp, mean_and_sd)
  ) %>% 
  select(-samp)
```

## What about something more realistic...

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's nest within weather stations...

```{r}
weather_nest_df = 
  weather_df %>% 
  nest(data = date:tmin)
```

Really is a list column!

```{r}
weather_nest_df[["data"]]
```

```{r}
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest_df[["data"]][[3]])
```

Let's write a short lil ol function

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest_df[["data"]][[1]])

map(weather_nest_df[["data"]], weather_lm)
```

Can I do all this in a tidy way

```{r}
weather_nest_df %>% 
  mutate(
    model = map(data, weather_lm)
  )
```

YUP



unnesting

```{r}
weather_nest_df %>% 
  unnest(data)
```

```{r}
read_page_reviews = function(url){
  
  dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)

reviews = 
  tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
  )

reviews
}
```


```{r}
base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(base_url, 1:5)

```


```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

```{r}
dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(base_url, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()
```

